PineAPPL:\\ combining EW and QCD corrections for PDF fits

### 2020-08-08 paper/sec-results.tex
Use SI macros for percentages

\paragraph{Numerical results.}
We first consider the single-differential measurement at a high lepton-pair
invariant mass performed by the ATLAS experiment at \SI{7}{\tera\electronvolt}.
From figure~\ref{fig:atlaszhighmass49fb} we immediately
observe that the validation of the \textsc{PineAPPL} result against the MC
result is successful. The relative difference between the two is of the order
$0.1\tcperthousand$ at most, with negligible fluctuations across different
invariant mass bins. The agreement is similarly good irrespective of the
perturbative accuracy of the theory (NLO QCD or NLO QCD+EW) or of the scale
choice.

@@

In figure~\ref{fig:atlastop} we report the
distributions differential in the transverse momentum of the top quark,
$p_\mathrm{T}^\mathrm{t}$, and in the invariant mass of the top-quark pair,
$m_{\mathrm{t}\bar{\mathrm{t}}}$. Analogous plots for the distributions differential
in the rapidity of either the top quark or the top-quark pair are collected in
appendix~\ref{app:add_plots}. From figure~\ref{fig:atlastop}, we immediately
validate the \textsc{PineAPPL} result: its relative difference with respect to
the MC result is at most as large as $0.4\tcperthousand$, irrespective of the
accuracy of the theory, of the choice of scale and of the distribution
considered.

@@

The process receives its leading contribution from the $\mathrm{gg}$ channel,
which varies between 81\% and 61\% (76\% and 83\%) of the $p_\mathrm{T}^\mathrm{t}$
($m_{\mathrm{t}\bar{\mathrm{t}}}$) differential cross section as the value of the
transverse momentum of the top quark (the invariant mass of the top-quark pair)
increases; the largest PI contribution for this process is $\gamma\mathrm{g}$ scattering,
which accounts for about 0.5\% -- 1\% (0.5\% -- 0.7\%) of the cross
section, and is almost entirely (90\%) due to the LO contribution at $\mathcal{O}(\alphas\alpha)$; the contribution from other PI parton luminosities is comparatively
negligible. Overall, the EW corrections suppress the $p_\mathrm{T}^\mathrm{t}$
($m_{\mathrm{t}\bar{\mathrm{t}}}$) distribution by about 0.2\% -- 3.5\%
(0.5\% -- 0.2\%) for increasing values of $p_\mathrm{T}^\mathrm{t}$
($m_{\mathrm{t}\bar{\mathrm{t}}}$), except in the first bin of the
$p_\mathrm{T}^\mathrm{t}$ distribution, where they enhance the cross section by
about 1\%. The size of these shifts, however, remains always significantly
smaller than the data uncertainty.\footnote{In
  figure~\ref{fig:atlastop} the data uncertainty corresponds to the ATLAS
  measurement~\cite{Aad:2015auj}. Similar considerations apply also for the CMS
  measurement~\cite{Khachatryan:2015oaa}.}
As a consequence, we anticipate that the more accurate NLO QCD+EW theory is
likely to be easily accommodated by the large data uncertainty, should the data
be fitted with the inclusion of EW corrections; PDFs will possibly not become
more precise.

>>>>

\paragraph{Numerical results.}
We first consider the single-differential measurement at a high lepton-pair
invariant mass performed by the ATLAS experiment at \SI{7}{\tera\electronvolt}.
From figure~\ref{fig:atlaszhighmass49fb} we immediately
observe that the validation of the \textsc{PineAPPL} result against the MC
result is successful. The relative difference between the two is of the order
\SI{0.1}{\permille} at most, with negligible fluctuations across different
invariant mass bins. The agreement is similarly good irrespective of the
perturbative accuracy of the theory (NLO QCD or NLO QCD+EW) or of the scale
choice.

@@

In figure~\ref{fig:atlastop} we report the
distributions differential in the transverse momentum of the top quark,
$p_\mathrm{T}^\mathrm{t}$, and in the invariant mass of the top-quark pair,
$m_{\mathrm{t}\bar{\mathrm{t}}}$. Analogous plots for the distributions differential
in the rapidity of either the top quark or the top-quark pair are collected in
appendix~\ref{app:add_plots}. From figure~\ref{fig:atlastop}, we immediately
validate the \textsc{PineAPPL} result: its relative difference with respect to
the MC result is at most as large as \SI{0.4}{\permille}, irrespective of the
accuracy of the theory, of the choice of scale and of the distribution
considered.

@@

The process receives its leading contribution from the $\mathrm{gg}$ channel,
which varies between \SI{81}{\percent} and \SI{61}{\percent} (\SI{76}{\percent} and \SI{83}{\percent}) of the $p_\mathrm{T}^\mathrm{t}$
($m_{\mathrm{t}\bar{\mathrm{t}}}$) differential cross section as the value of the
transverse momentum of the top quark (the invariant mass of the top-quark pair)
increases; the largest PI contribution for this process is $\gamma\mathrm{g}$ scattering,
which accounts for about \SIrange{0.5}{1}{\percent} (\SIrange{0.5}{0.7}{\percent}) of the cross
section, and is almost entirely (\SI{90}{\percent}) due to the LO contribution at $\mathcal{O}(\alphas\alpha)$; the contribution from other PI parton luminosities is comparatively
negligible. Overall, the EW corrections suppress the $p_\mathrm{T}^\mathrm{t}$
($m_{\mathrm{t}\bar{\mathrm{t}}}$) distribution by about \SIrange{0.2}{3.5}{\percent}
(\SIrange{0.5}{0.2}{\percent}) for increasing values of $p_\mathrm{T}^\mathrm{t}$
($m_{\mathrm{t}\bar{\mathrm{t}}}$), except in the first bin of the
$p_\mathrm{T}^\mathrm{t}$ distribution, where they enhance the cross section by
about \SI{1}{\percent}. The size of these shifts, however, remains always significantly
smaller than the data uncertainty.\footnote{In
  figure~\ref{fig:atlastop} the data uncertainty corresponds to the ATLAS
  measurement~\cite{Aad:2015auj}. Similar considerations apply also for the CMS
  measurement~\cite{Khachatryan:2015oaa}.}
As a consequence, we anticipate that the more accurate NLO QCD+EW theory is
likely to be easily accommodated by the large data uncertainty, should the data
be fitted with the inclusion of EW corrections; PDFs will possibly not become
more precise.
